Outputs from time slice analyses

### 2017-12-06 analyses/04-stats.Rmd
corrected peak ages

```{r, eval = TRUE, message = FALSE}
library(tidyverse)
library(broom)
library(dispRity)
```

@@

```{r, warning = FALSE}
# ages
strat <- out1$results$stratigraphy
duration <- out1$results$duration
number <- out1$results$number

>>>>

```{r, eval = TRUE, message = FALSE}
library(tidyverse)
library(broom)
library(dispRity)
source("../functions/stats_fun.R")
```

@@

```{r, warning = FALSE}

## Getting the max/min for each age/epoch
age_results_max <- do.call(rbind, lapply(out1$objects, select.max.min.method, fun = max))
age_results_min <- do.call(rbind, lapply(out1$objects, select.max.min.method, fun = min))
epoch_results_max <- do.call(rbind, lapply(out1$objects, select.max.min.method, fun = max))
epoch_results_min <- do.call(rbind, lapply(out1$objects, select.max.min.method, fun = min))

## Combining into the nice table formats
age_results_max <- cbind(age_results_max, "stratigraphy" = rep("Age", nrow(age_results_max)),
                         "bin_type" = unlist(strsplit(rownames(age_results_max), split = "\\..*")))
age_results_min <- cbind(age_results_min, "stratigraphy" = rep("Age", nrow(age_results_min)),
                         "bin_type" = unlist(strsplit(rownames(age_results_min), split = "\\..*")))
epoch_results_max <- cbind(epoch_results_max, "stratigraphy" = rep("Epoch", nrow(epoch_results_max)),
                        "bin_type" = unlist(strsplit(rownames(epoch_results_max), split = "\\..*")))
epoch_results_min <- cbind(epoch_results_min, "stratigraphy" = rep("Epoch", nrow(epoch_results_min)),
                        "bin_type" = unlist(strsplit(rownames(epoch_results_min), split = "\\..*")))

## Combining the age and epoch results together
all_peaks_max <- rbind(age_results_max, epoch_results_max)
all_peaks_min <- rbind(age_results_min, epoch_results_min)

write.csv(all_peaks_max, file = paste0("../outputs/peaks.max.", slug, ".csv"), quote = FALSE, 
          row.names = FALSE)

write.csv(all_peaks_min, file = paste0("../outputs/peaks.min.", slug, ".csv"), quote = FALSE, 
          row.names = FALSE)
```

<!-- former version -->

```{r, eval = FALSE, echo = FALSE}
# ages
strat <- out1$results$stratigraphy
duration <- out1$results$duration
number <- out1$results$number
